Курсовая работа по теме \\ \Huge{«Методы оптимизации»}

### 2008-12-13 simplex-method.tkz.tex
Added contour lines

\begin{figure}[!thb]
  \centering
  \begin{tikzpicture}
    \begin{axis}[      
      xlabel=$x_1$,
      ylabel=$x_2$,
      xtick={1, 5}, ytick={1, 2, 5},
      xmin=-0.5, ymin=-0.5,
      xmax=7, ymax=7,
      axis x line=center,
      axis y line=center,
      pattern color=gray]

      \addplot[draw=none,mark=none,pattern=north east lines] coordinates{
        (0,0) (0,2) (2,3.5) (5,0)} \closedcycle;

      \addplot[thick,mark=none] coordinates{(4, 5) (-1, 1.25)};
      \addplot[thick,mark=none] coordinates{(5.5, -0.5833) (1.5, 4.0833)};
      \draw node[circle, fill=black, scale=0.5, 
                 pin={above:$(2, 3.5)$}] at (axis cs:2,3.5) {};

>>>>

\begin{figure}[!thb]
  \centering
  \begin{tikzpicture}
    \begin{axis}[      
      xlabel=$x_1$,
      ylabel=$x_2$,
      xtick={1, 2, 3, 4, 5, 6},
      ytick={1, 3, 4, 5},
      xmin=-2, ymin=-1,
      xmax=7, ymax=7,
      axis x line=center,
      axis y line=center,
      pattern color=gray,
      area legend]

      \addplot[draw=none,mark=none,pattern=north east lines] coordinates{
        (0,0) (0,2) (2,3.5) (5,0)} \closedcycle;
      \label{plot:simplex-feasible-space}

      \input{simplex_prob-contours.tkz.tex}

      \addplot[thick,mark=none] coordinates{(4, 5) (-1, 1.25)};
      \addplot[thick,mark=none] coordinates{(5.5, -0.5833) (1.5, 4.0833)};
      \draw node[circle, fill=black, scale=0.5, 
                 pin={above:$(2, 3.5)$}] at (axis cs:2,3.5) {};
      \draw node[circle, fill=black, scale=0.5, 
                 pin={above left:$(0, 2)$}] at (axis cs:0,2) {};
